Fabric-Elasticity Relationships of Tibial Trabecular Bone are Similar in Osteogenesis Imperfecta and Healthy Individuals

### 2021-06-30 09_Article/Simon_2021_Bone_Draft_V02.tex

Osteogenesis imperfecta (OI), commonly known as brittle bone disease, is an inherited form of bone fragility \cite{Tournis2018}. OI prevalence is estimated at about  1/13,500 of births, less severe forms not being accounted in this estimation as they are recognized later in life \cite{Lindahl2015}. Therefore, OI is considered as a rare metabolic bone disorder. In most cases, OI is caused by mutations in genes encoding type I collagen (COL1A1 and COL1A2), leading to brittle and fragile bones \cite{LIM2017}, as well as deformed geometry and size in some cases. OI can be categorized according to disease severity \cite{Mortier2019}, the most familiar forms are:
\begin{itemize}
	\item Type I: mild
	\item Type II: perinatally lethal
	\item Type III: most severe surviving form
	\item Type IV: intermediate severity
\end{itemize}

Bone fragility in OI is complex and not totally understood, despite the investigations at different hierarchical levels. Multiple studies show that DXA areal bone mineral density (aBMD) tends to be lower in OI compared to healthy individuals \cite{Folkestad2012,Lindahl2015,Scheres2018}.  \citeauthor{Folkestad2012}\cite{Folkestad2012}, \citeauthor{Kocijan2015}\cite{Kocijan2015}, and \citeauthor{Rolvien2018}\cite{Rolvien2018} have shown that the microstructure is different as well, namely bone volume fraction (BV/TV) and trabecular number (Tb.N.) in OI bone is lower than for healthy controls. Trabecular separation (Tb.Sp.) and inhomogeneity (Tb.Sp.SD) are higher for individuals with OI but the trabecular thickness (Tb.Th.) is not significantly different. At the ECM level, a recent study showed that, in compression, OI bone tends to present higher modulus, ultimate stress and post-yield behavior than healthy bone, mostly affected by the higher degree of mineralization of OI bone \cite{Indermaur2021}.\\

>>>>

Osteogenesis imperfecta (OI), commonly known as brittle bone disease, is an inherited form of bone fragility \cite{Tournis2018}. OI prevalence is estimated at about  1/13,500 of births, less severe forms not being accounted in this estimation as they are recognized later in life \cite{Lindahl2015}. Therefore, OI is considered as a rare metabolic bone disorder. In most cases, OI is caused by mutations in genes encoding type I collagen (COL1A1 and COL1A2), leading to brittle and fragile bones \cite{LIM2017}, as well as deformed geometry and size in some cases. OI can be categorized according to disease severity \cite{Mortier2019}, where most familiar forms are:
\begin{itemize}
	\item Type I: mild
	\item Type II: perinatally lethal
	\item Type III: most severe surviving form
	\item Type IV: intermediate severity
\end{itemize}

Bone fragility in OI is complex and not totally understood, despite the investigations at different hierarchical levels. Multiple studies show that DXA areal bone mineral density (aBMD) tends to be lower in OI compared to healthy individuals \cite{Folkestad2012,Lindahl2015,Scheres2018}.  \citeauthor{Folkestad2012}\cite{Folkestad2012}, \citeauthor{Kocijan2015}\cite{Kocijan2015}, and \citeauthor{Rolvien2018}\cite{Rolvien2018} have shown that the microstructure is different as well. Bone volume fraction (BV/TV) and trabecular number (Tb.N.) in OI bone is lower than for healthy controls. Trabecular separation (Tb.Sp.) and inhomogeneity (Tb.Sp.SD) are higher for individuals with OI compared to healthy control, and the trabecular thickness (Tb.Th.) is not significantly different. At the ECM level, a recent study showed that, in compression, OI bone tends to present higher modulus, ultimate stress and post-yield behavior than healthy bone, mostly affected by the higher degree of mineralization of OI bone \cite{Indermaur2021}.\\
